Memristor-based recurrent modules for neural computing

### 2023-11-30 paper/circuit.tex
fixed paper

The system will be working with a $V_{dd}$ of $1.8V$. Such a value was chosen because this is a low power system.

The way values are encoded in the analog system will be descibed here as it serves for the entire thesis.
In order for the system to support negative numbers we're going to use a $V_{cm}$ set to $\frac{V_{dd}}{2}$. That means that $V_{cm}=\frac{V_{dd}}{2}=0.9V$. This $V_{cm}$ will then describe a zero. A step of one was chosen to be $0.1V$ in the analog circuit.
\Cref{tab:valConv} shows the conversions from a real number to its voltage equivalent.

\begin{table}[b]
  \caption{Real/Voltage Conversion Table.}
  \label{tab:valConv}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \textbf{Real value} & \textbf{Voltage} \\
    \hline
    $0$ & $0.9V$ \\
    \hline
    $1$ & $1.0V$ \\
    \hline
    $x$ & $V(x)=\frac{x}{10}+V_{cm}$\\
    \hline
    $real(v)=(v-0.9)\cdot 10$ & $v$\\
    \hline
  \end{tabular}
\end{table}

Since the system cannot reach voltage outside of the operating range with the intended behavior, the voltage is then restricted to $V\in [0,1.8]$. This means that the range of real value that the systems can handle is $x\in [-9,9]$.

@@

\begin{table}[t]
  \caption{Circuits parameters}
  \label{tab:afPar}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    \textbf{Parameter} & \textbf{Sigmoid} & \textbf{\ac{tanh}} \\
    \hline
    $V_1$ & \multicolumn{2}{c|}{$1.1V$}\\
    \hline
    $V_2$ & \multicolumn{2}{c|}{$635mV$}\\
    \hline
    $V_3$ & $0.8V$ & $550mV$\\
    \hline
    $i_{dc}$ & \multicolumn{2}{c|}{$150uA$}\\
    \hline
    $w$ & \multicolumn{2}{c|}{$900nm$}\\
    \hline
    $l$ & \multicolumn{2}{c|}{$60nm$}\\
    \hline
    $R_1$ & \multicolumn{2}{c|}{$5k\Omega$}\\
    \hline
    $R_2$ & \multicolumn{2}{c|}{$10k\Omega$}\\
    \hline
    $R_3$ & $2k\Omega$ & $4k\Omega$\\
    \hline
  \end{tabular}
\end{table}

@@

In this work, the choice was made to use a two memristor per synapse architecture. Using two memristor per synapse doubles the area but doubles the weight range \cite{doubleMem} and allows to easily use negavite weights. The output voltage will be centered around $V_{cm}$ and be compliant with the standard set in \cref{tab:valConv}.

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means its conductance range is $ G \in [ G_{min}, G_{max}]$ (with $ G_{min}= \frac{1}{R_{max}}$ and $ G_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works. A simplified version of the double memristors per synapse circuit is also available in \cref{circt:doubleMem}.

@@

Using $x_k$ as the voltage for the input line $k$. The highest \ac{opAmp} is identified as $opAmp_0$ and the lowest $opAmp_1$.

For the sake of simplicity, the following equations considers the ground to be $V_{cm}$.

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp_0}=-R_r\cdot i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp_0}}{R_r}=i_--i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem2}
  \begin{array}{2}
    V_{opAmp_1}=y_0=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)\\
    =R_f\cdot\sum_{k=0}^n( G_{k+}- G_{k-})\cdot x_k
  \end{array}
\end{equation}
With $i_+=\sum_{k=0}^n G_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n G_{k-}\cdot x_k$.

@@

\begin{equation}\label{eq:finalVoltMult}
  V_{out}=10\cdot(V_{in_1}-V_{cm})\cdot (V_{in_2}-V_{cm}) + V_{cm}
\end{equation}

@@

\begin{equation}\label{eq:voltMult}
  V_{voltMult}=-(V_{in_1}-V_{cm})\cdot (V_{in_2}-V_{cm}) + V_{cm}
\end{equation}
\begin{equation}\label{eq:invAmp}
  V_{out}=-(V_{voltMult}-V_{cm})\cdot10+V_{cm}
\end{equation}

Where $V_{out}$ is the output voltage the inverting amplifier, $V_{voltMult}$ is the out voltage of the voltage multiplier itself and $V_{in_1}$ and $V_{in_2}$ are the input voltages.

@@

\begin{itemize}
  \item $\overrightarrow{z_t}$ is the input of the crossbar but not the input of the \ac{LSTM}. It is defined by $\overrightarrow{z_t}=(\overrightarrow{x_t},\overrightarrow{h_{t-1}},\overrightarrow{b})$.
  \item $e_{j,0}$ and $e_{j,1}$ are two enable flags that respectively represent the first and second half of $e_j$.
  \item $e_{in}$ and $e_{out}$ are the flags used to enable the hidden state values to go to the input (feedback connection) or to the output of the circuit.
  \item $e_{next}$ is the enable flag on in between two time steps.
  \item $R_{amp0}$ and $R_{amp1}$ are the two resistances used to amplify the output voltage of the voltage multipliers. Their value is set so that $\frac{R_{amp1}}{R_{amp0}}=10$.
\end{itemize}

@@

The GRU equations requires to compute the function defined in \cref{eq:1minus0}.
\begin{equation}\label{eq:1minus0}
  f(x)=1-x
\end{equation}
The solution found to do compute the operation consist of using an \ac{opAmp} as an inverter around $V_{inv}$, the formula is available in \cref{eq:1minus1}.
\begin{equation}\label{eq:1minus1}
  f_v(v)=-(v-V_{inv})+V_{inv}=2\cdot V_{inv} -v
\end{equation}
With $V_{inv}=V_{cm}+0.05$.

>>>>

The system will be working with a $\symv_{dd}$ of $1.8V$. Such a value was chosen because this is a low power system.

The way values are encoded in the analog system will be descibed here as it serves for the entire thesis.
In order for the system to support negative numbers we're going to use a $\symv_{cm}$ set to $\frac{\symv_{dd}}{2}$. That means that $\symv_{cm}=\frac{\symv_{dd}}{2}=0.9V$. This $\symv_{cm}$ will then describe a zero. A step of one was chosen to be $0.1V$ in the analog circuit.
\Cref{tab:valConv} shows the conversions from a real number to its voltage equivalent.

\begin{table}[b]
  \caption{Real/Voltage Conversion Table.}
  \label{tab:valConv}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \textbf{Real value} & \textbf{Voltage} \\
    \hline
    $0$ & $0.9V$ \\
    \hline
    $1$ & $1.0V$ \\
    \hline
    $x$ & $\symv(x)=\frac{x}{10}+\sym_{cm}$\\
    \hline
    $real(\symv)=(\symv-\symv_{cm})\cdot 10$ & $\symv$\\
    \hline
  \end{tabular}
\end{table}

Since the system cannot reach voltage outside of the operating range with the intended behavior, the voltage is then restricted to $\symv\in [0,1.8]$. This means that the range of real value that the systems can handle is $x\in [-9,9]$.

@@

\begin{table}[t]
  \caption{Circuits parameters}
  \label{tab:afPar}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    \textbf{Parameter} & \textbf{Sigmoid} & \textbf{\ac{tanh}} \\
    \hline
    $\symv_1$ & \multicolumn{2}{c|}{$1.1V$}\\
    \hline
    $\symv_2$ & \multicolumn{2}{c|}{$635mV$}\\
    \hline
    $\symv_3$ & $0.8V$ & $550mV$\\
    \hline
    $\symi_{dc}$ & \multicolumn{2}{c|}{$150uA$}\\
    \hline
    $w$ & \multicolumn{2}{c|}{$900nm$}\\
    \hline
    $l$ & \multicolumn{2}{c|}{$60nm$}\\
    \hline
    $\symR_1$ & \multicolumn{2}{c|}{$5k\Omega$}\\
    \hline
    $\symR_2$ & \multicolumn{2}{c|}{$10k\Omega$}\\
    \hline
    $\symR_3$ & $2k\Omega$ & $4k\Omega$\\
    \hline
  \end{tabular}
\end{table}

@@

In this work, the choice was made to use a two memristor per synapse architecture. Using two memristor per synapse doubles the area but doubles the weight range \cite{doubleMem} and allows to easily use negavite weights. The output voltage will be centered around $\symv_{cm}$ and be compliant with the standard set in \cref{tab:valConv}.

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $\symR\in[\symR_{min},\symR_{max}]$, that means its conductance range is $ \symG \in [ \symG_{min}, \symG_{max}]$ (with $ \symG_{min}= \frac{1}{\symR_{max}}$ and $ \symG_{max}= \frac{1}{\symR_{min}}$). This design works using two \ac{opAmp} connected to $\symv_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works. A simplified version of the double memristors per synapse circuit is also available in \cref{circt:doubleMem}.

@@

Using $\symv_k$ as the voltage for the input line $k$. The highest \ac{opAmp} is identified as $opAmp_0$ and the lowest $opAmp_1$.

For the sake of simplicity, the following equations considers the ground to be $\symv_{cm}$.

\begin{equation}
  \label{eq:doubleMem0}
  \symv_{opAmp_0}=-\symR_r\cdot \symi_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  \symi_{\symR_f}=\symi_-+\frac{\symv_{opAmp_0}}{\symR_r}=\symi_--\symi_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem2}
  \begin{array}{2}
    \symv_{opAmp_1}=\symv_{out}=-\symR_f\cdot(\symi_--\symi_+)=\symR_f\cdot(\symi_+-\symi_-)\\
    =\symR_f\cdot\sum_{k=0}^n( \symG_{k+}- \symG_{k-})\cdot \symv_k
  \end{array}
\end{equation}
With $\symi_+=\sum_{k=0}^n \symG_{k+}\cdot \symv_k$ and $\symi_-=\sum_{k=0}^n \symG_{k-}\cdot \symv_k$.

@@

\begin{equation}\label{eq:finalVoltMult}
  \symv_{out}=10\cdot(\symv_{in_1}-\symv_{cm})\cdot (\symv_{in_2}-\symv_{cm}) + \symv_{cm}
\end{equation}

@@

\begin{equation}\label{eq:voltMult}
  \symv_{voltMult}=-(\symv_{in_1}-\symv_{cm})\cdot (\symv_{in_2}-\symv_{cm}) + \symv_{cm}
\end{equation}
\begin{equation}\label{eq:invAmp}
  \symv_{out}=-(\symv_{voltMult}-\symv_{cm})\cdot10+\symv_{cm}
\end{equation}

Where $\symv_{out}$ is the output voltage the inverting amplifier, $\symv_{voltMult}$ is the out voltage of the voltage multiplier itself and $\symv_{in_1}$ and $\symv_{in_2}$ are the input voltages.

@@

\begin{itemize}
  \item $\overrightarrow{z_t}$ is the input of the crossbar but not the input of the \ac{LSTM}. It is defined by $\overrightarrow{z_t}=(\overrightarrow{x_t},\overrightarrow{h_{t-1}},\overrightarrow{b})$.
  \item $e_{j,0}$ and $e_{j,1}$ are two enable flags that respectively represent the first and second half of $e_j$.
  \item $e_{in}$ and $e_{out}$ are the flags used to enable the hidden state values to go to the input (feedback connection) or to the output of the circuit.
  \item $e_{next}$ is the enable flag on in between two time steps.
  \item $\symR_{amp0}$ and $\symR_{amp1}$ are the two resistances used to amplify the output voltage of the voltage multipliers. Their value is set so that $\frac{\symR_{amp1}}{\symR_{amp0}}=10$.
\end{itemize}

@@

The GRU equations requires to compute the function defined in \cref{eq:1minus0}.
\begin{equation}\label{eq:1minus0}
  f(x)=1-x
\end{equation}
The solution found to do compute the operation consist of using an \ac{opAmp} as an inverter around $V_{inv}$, the formula is available in \cref{eq:1minus1}.
\begin{equation}\label{eq:1minus1}
  f_v(\symv)=-(\symv-\symv_{inv})+\symv_{inv}=2\cdot \symv_{inv} -\symv
\end{equation}
With $\symv_{inv}=\symv_{cm}+0.05$.

### 2023-11-30 paper/state.tex
fixed paper

The feedback connection is caracterized by the hidden state vector ($\overrightarrow{h_t}$) which serves as the output and as part of the input for the next time step, a RNN is defined as \cref{eq:rnn}.

\begin{equation}\label{eq:rnn}
  \overrightarrow{h_t}=f(\overrightarrow{x_t},\overrightarrow{h_{t-1}})
\end{equation}

@@

\begin{equation}\label{eq:srnn}
  \overrightarrow{h_t}=tanh([\overrightarrow{x_t},\overrightarrow{h_{t-1}}]\cdot w + \overrightarrow{b})
\end{equation}

Where ($w$,$\overrightarrow{b}$) are the pair of weights matrix and bias vectors. $\overrightarrow{x_t}$ is the input vector and $\overrightarrow{h_t}$ is the hidden state vector.

@@

LSTMs are a type of RNN used to solve the vanishing gradiant problem \cite{firstLSTM}. It was improved a few times before becoming the modern LSTM \cite{improvLSTM}. The LSTM differs from a simple RNN because of its second feedback variable being the cell state ($\overrightarrow{c_t}$).

@@

\begin{equation}\label{eq:inputG}
  \overrightarrow{i_t}= G ([\overrightarrow{x_{t_1}},\overrightarrow{h_{t-1}}]\cdot w_i + \overrightarrow{b_i})
\end{equation}
\begin{equation}\label{eq:forgetG}
  \overrightarrow{f_t}= G ([\overrightarrow{x_{t_1}},\overrightarrow{h_{t-1}}]\cdot w_f + \overrightarrow{b_f})
\end{equation}
\begin{equation}\label{eq:outputG}
  \overrightarrow{o_t}= G ([\overrightarrow{x_{t_1}},\overrightarrow{h_{t-1}}]\cdot w_o + \overrightarrow{b_o})
\end{equation}
\begin{equation}\label{eq:candCell}
  \overrightarrow{\tilde{c}_t}=tanh([\overrightarrow{x_{t_1}},\overrightarrow{h_{t-1}}]\cdot w_c+ \overrightarrow{b_c})
\end{equation}

@@

\begin{equation}\label{eq:cellS}
  \overrightarrow{c_t}=\overrightarrow{f_t}\odot \overrightarrow{c_{t-1}} + \overrightarrow{i_t} \odot \overrightarrow{\tilde{c}_t}
\end{equation}

@@

\begin{equation}\label{eq:hiddenS}
  \overrightarrow{h_t}=\overrightarrow{o_t}\odot tanh(\overrightarrow{c_t})
\end{equation}

Where ($w_i$,$\overrightarrow{b_i}$), ($w_f$,$\overrightarrow{b_f}$), ($w_o$,$\overrightarrow{b_o}$) and ($w_c$,$\overrightarrow{b_c}$) are the pair of weights matrixes and bias vectors for the input, forget, output and candidate cell gates respectively. $\overrightarrow{x_t}$ is the input vector and $\overrightarrow{h_t}$ is the hidden state vector.

@@

\begin{equation}\label{eq:updateG}
  \overrightarrow{z_t}= G ([\overrightarrow{x_t},\overrightarrow{h_{t-1}}] \cdot w_z + \overrightarrow{b_z})
\end{equation}
\begin{equation}\label{eq:resetG}
  \overrightarrow{r_t}= G ([\overrightarrow{x_t},\overrightarrow{h_{t-1}}] \cdot w_r + \overrightarrow{b_r})
\end{equation}
\begin{equation}\label{eq:candActivG}
  \overrightarrow{\hat{h_t}}=tanh(\overrightarrow{x_t}\cdot w_{hx}+(\overrightarrow{r_t}\odot\overrightarrow{h_{t-1}}) \cdot w_{hh} + \overrightarrow{b_h})
\end{equation}
\begin{equation}\label{eq:gruHidG}
  \overrightarrow{h_t}=(\overrightarrow{1}-\overrightarrow{z_t})\odot \overrightarrow{h_{t-1}} + \overrightarrow{z_t}\odot \overrightarrow{\hat{h_t}}
\end{equation}

Where ($w_z$,$\overrightarrow{b_z}$), ($w_r$,$\overrightarrow{b_r}$),($w_{hx}$,$w_{hh}$,$\overrightarrow{b_h}$) are the weights matrixes and bias vectors for the update, reset and candidate activation gates respectively.

@@

Memristors are the lesser known fourth fundamental passive component of electronics, among resistors, capacitors and inductor.
It was first theorized in 1971 as a missing fundamental component in \cite{TheoMemristor}. The name comes from the blend of \textit{memory} and \textit{resistance}.
The missing component linking the four fundamental circuit variables, voltage ($v$), charge ($q$), current ($i$) and flux ($\phi$). \Cref{fig:fundComp} shows the four fundamental variables are on each side of the square, with the ones on opposite sides being linked by the following equations :

\begin{equation}
  d\phi = v\cdot dt
\end{equation}

\begin{equation}
  dq = i\cdot dt
\end{equation}

Resistors, capacitors and inductors were already very established and well known components, so it was theorized that a fourth device should then exist to physically link flux ($\phi$) and charge ($q$).  The flux in this case is not a magnetic flux and is defined as such : $ d\phi=v\cdot dt \Rightarrow \phi =  \int v \,dt  $.

@@

\begin{figure}[t]
  \centering
  \includesvg[wdith=0.4\columnwidth,pretex=\scriptsize]{crossbar/node}
  %\def\svgheigth{3.5cm}
  %\input{crossbar/node.pdf_tex}
  \caption{Memristor crossbar node of the $i^{th}$ line and $j^{th}$ column}
  \label{fig:crossNode}
\end{figure}

A voltage is applied on the $i^{th}$ line, and because every column is virtually grounded, the voltage applied to the memristor, with resistance $R_i$, is $V_i$. By applying Ohm's law, we know that the current flowing into the memristor ($I_{i}$) is bound by the following equation :

\begin{equation}
  V_i = R\cdot I_{i} \Rightarrow I_{i} = V_i\cdot (\frac{1}{R_i})= V_i\cdot G_i
\end{equation}
With $ G_i$ being the conductance of memristor, defined as $ G_i=\frac{1}{R_i}$.

This line then joins the column where a current of $I_{i,j-1}$ is flowing, then according to Kirchhoff's current law the resulting current is :
\begin{equation}
  I_{j,i} = I_{j,i-1}+I_{i} = I_{j,i-1} + V_i\cdot G_i
\end{equation}
Unfolding the equations will give the current at the bottom of the column, for example, the current at the bottom of the first column in \cref{fig:crossbar} is :
\begin{equation}
  I_1= G_1\cdot V_1 +  G_2\cdot V_2 +  G_3\cdot V_3
\end{equation}
With $ G_1$, $ G_2$ and $ G_3$ being the conductance of the 3 memristors in the first column.

>>>>

The feedback connection is caracterized by the hidden state vector ($\symvh_t$) which serves as the output and as part of the input for the next time step, a RNN is defined as \cref{eq:rnn}.

\begin{equation}\label{eq:rnn}
  \symvh_t=f(\symvx_t,\symvh_{t-1})
\end{equation}

@@

\begin{equation}\label{eq:srnn}
  \symvh_t=tanh([\symvx_t,\symvh_{t-1}]\cdot \symmw + \symvb)
\end{equation}

Where (\symmw,\symvb) are the pair of weights matrix and bias vectors. $\symvx_t$ is the input vector and $\symvh_t$ is the hidden state vector.

@@

LSTMs are a type of RNN used to solve the vanishing gradiant problem \cite{firstLSTM}. It was improved a few times before becoming the modern LSTM \cite{improvLSTM}. The LSTM differs from a simple RNN because of its second feedback variable being the cell state ($\symvc_t$).

@@

\begin{equation}\label{eq:inputG}
  \symvi_t= \sigma([\symvx_{t_1},\symvh_{t-1}]\cdot \symmw_i + \symvb_i)
\end{equation}
\begin{equation}\label{eq:forgetG}
  \symvf_t= \sigma([\symvx_{t_1},\symvh_{t-1}]\cdot \symmw_f + \symvb_f)
\end{equation}
\begin{equation}\label{eq:outputG}
  \symvo_t= \sigma([\symvx_{t_1},\symvh_{t-1}]\cdot \symmw_o + \symvb_o)
\end{equation}
\begin{equation}\label{eq:candCell}
  \symvct_t=tanh([\symvx_{t_1},\symvh_{t-1}]\cdot \symmw_c+ \symvb_c)
\end{equation}

@@

\begin{equation}\label{eq:cellS}
  \symvc_t=\symvf_t\odot \symvc_{t-1} + \symvi_t \odot \symvct_t
\end{equation}

@@

\begin{equation}\label{eq:hiddenS}
  \symvh_t=\symvo_t\odot tanh(\symvc_t)
\end{equation}

Where ($\symmw_i$,$\symvb_i$), ($\symmw_f$,$\symvb_f$), ($\symmw_o$,$\symvb_o$) and ($\symmw_c$,$\symvb_c$) are the pair of weights matrixes and bias vectors for the input, forget, output and candidate cell gates respectively. $\symvx_t$ is the input vector and $\symvh_t$ is the hidden state vector.

@@

\begin{equation}\label{eq:updateG}
  \symvz_t= \sigma([\symvx_t,\symvh_{t-1}] \cdot \symmw_z + \symvb_z)
\end{equation}
\begin{equation}\label{eq:resetG}
  \symvr_t= \sigma([\symvx_t,\symvh_{t-1}] \cdot \symmw_r + \symvb_r)
\end{equation}
\begin{equation}\label{eq:candActivG}
  \symvhh_t=tanh(\symvx_t\cdot \symmw_{hx}+(\symvr_t\odot\symvh_{t-1}) \cdot \symmw_{hh} + \symvb_h)
\end{equation}
\begin{equation}\label{eq:gruHidG}
  \symvh_t=(\vunit-\symvz_t)\odot \symvh_{t-1} + \symvz_t\odot \symvhh_t
\end{equation}

Where ($\symmw_z$,$\symvb_z$), ($\symmw_r$,$\symvb_r$),($\symmw_{hx}$,$\symmw_{hh}$,$\symvb_h$) are the weights matrixes and bias vectors for the update, reset and candidate activation gates respectively.

@@

Memristors are the lesser known fourth fundamental passive component of electronics, among resistors, capacitors and inductor.
It was first theorized in 1971 as a missing fundamental component in \cite{TheoMemristor}. The name comes from the blend of \textit{memory} and \textit{resistance}.
The missing component linking the four fundamental circuit variables, voltage (\symv), charge (\symq), current (\symi) and flux (\symphi). \Cref{fig:fundComp} shows the four fundamental variables are on each side of the square, with the ones on opposite sides being linked by the following equations :

\begin{equation}
  d\symphi = \symv\cdot d\symt
\end{equation}

\begin{equation}
  d\symq = \symi\cdot d\symt
\end{equation}

Resistors, capacitors and inductors were already very established and well known components, so it was theorized that a fourth device should then exist to physically link flux (\symphi) and charge (\symq).  The flux in this case is not a magnetic flux and is defined as such : $ d\symphi=\symv\cdot d\symt \Rightarrow \symphi =  \int \symv \,d\symt  $.

@@

\begin{figure}[t]
  \centering
  \includesvg[wdith=0.4\columnwidth,pretex=\scriptsize]{crossbar/node}
  %\def\svgheigth{3.5cm}
  %\input{crossbar/node.pdf_tex}
  \caption{Memristor crossbar node of the $k^{th}$ line and $j^{th}$ column}
  \label{fig:crossNode}
\end{figure}

A voltage is applied on the $k^{th}$ line, and because every column is virtually grounded, the voltage applied to the memristor, with resistance $R_i$, is $V_i$. By applying Ohm's law, we know that the current flowing into the memristor ($\symi_{k}$) is bound by the following equation :

\begin{equation}
  \symv_k = \symR\cdot \symi_{k} \Rightarrow \symi_{k} = \symv_k\cdot (\frac{1}{\symR_k})= \symv_k\cdot \symG_k
\end{equation}
With $ \symG_k$ being the conductance of memristor, defined as $ \symG_k=\frac{1}{\symR_k}$.

This line then joins the column where a current of $\symi_{j,k-1}$ is flowing, then according to Kirchhoff's current law the resulting current is :
\begin{equation}
  \symi_{j,k} = \symi_{j,k-1}+\symi_{k} = \symi_{j,k-1} + \symv_k\cdot \symG_k
\end{equation}
Unfolding the equations will give the current at the bottom of the column, for example, the current at the bottom of the first column in \cref{fig:crossbar} is :
\begin{equation}
  \symi_1= \symG_1\cdot \symv_1 +  \symG_2\cdot \symv_2 +  \symG_3\cdot \symv_3
\end{equation}
With $\symG_1$, $\symG_2$ and $\symG_3$ being the conductance of the 3 memristors in the first column.
